### 2019-06-04 thesis.tex
changes...

Considering the context presented above, the working proposal of
this PhD Thesis is to put forward the first numerical analysis of
the new weak turbulence theory for collisional plasmas \cite{YZKS16}
and explore its applications in the solar physics scope. In
\Cref{cha:theo-fram} and \Cref{cha:weak-turb}, we make a brief review
of the basic plasma kinetic theory equations and the weak turbulence
theory, respectively. In \Cref{noneigenmode}, we introduce the
new generalization of the weak turbulence theory, which takes into
account the contribution of noneigenmode fluctuations during the
derivation of the particle and wave kinetic equations, resulting
in three new terms. In \Cref{main}, we contextualize the present
work regarding the theory discussed in the previous chapter and
present the results obtained so far by appending the two papers
published in this subject. In \Cref{cha:final}, we summarize the
results and discuss the perspectives of the present research. Then,
we propose a schedule for the remaining period until the thesis
defense. In the end we have three appendices. \Cref{appA} shows
an improved approximation for the second order susceptibility of
the electrostatic bremsstrahlung for Langmuir waves. \Cref{appB}
presents a discussion about the asymptotic equilibrium state of the
Langmuir waves spectrum, considering a combination of a inverse
power-law kappa distribution and a Maxwellian distribution, in the
presence and in the absence of the electrostatic bremsstrahlung.
The discussion in \Cref{appB} is related with the article appended
in \Cref{appC}, which is a parallel research and is only slightly
related with the main subject of this work, that is the study of the
combined action of collective and collisional processes in weakly
turbulent plasmas, in the presence of electrostatic oscillations.

\section{Collective and collisional processes in plasmas}
\label{sec:collec-coll-proc}
In order to understand what collective processes are, one has to
have in mind that a plasma is a many-body system composed mostly
- or completely - of charged particles, that interact with each
other through electromagnetic forces. Due to the long range nature
of the electromagnetic forces, one charge can interact with several
charges at the same time, that will interact with others, and so
on. In such arrangement, the particle motion, at a certain volume
element of the plasma, will be affected not only by the surrounding
environment, but it will also be influenced by the conditions at
distant regions of the system. This nonlocal feature of the plasma
dynamics is called \emph{collective behavior} \cite{chen}.

Collective behavior is a necessary condition for an ionized to be
considered a plasma. As a fundamental characteristic, it occurs in
plasmas that exhibit overall neutrality, the so-called neutral
plasmas, and also in nonneutral plasmas.

\section{Kinetic theory}
\label{sec:kin-theo}
The kinetic theory is the most fundamental description of the
plasma dynamics. Based on the concepts and methods of statistical
mechanics, together with the Maxwell equations, it provides a
formal self-consistent evolution of the plasma processes. This
formalism takes into account the variations of the velocity
distribution function $f({\bf r},{\bf v},t)$ in the phase-space
for each particle species. Statistically, this means that the
product between the distribution function and the volume element
in the hexa-dimensional phase-space $f_\alpha({\bf r},{\bf v},t)d^3r d^3v$
represents the probability of finding a particle of species
$\alpha$ in a volume element $d^3r$ around ${\bf r}$ and in a
velocity volume element $d^3v$ around ${\bf v}$, at the instant
$t$ \cite{klimo,klimon}.

>>>>

% Considering the context presented above, the working proposal of
% this PhD Thesis is to put forward the first numerical analysis of
% the new weak turbulence theory for collisional plasmas \cite{YZKS16}
% and explore its applications in the solar physics scope. In
% \Cref{cha:theo-fram} and \Cref{cha:weak-turb}, we make a brief review
% of the basic plasma kinetic theory equations and the weak turbulence
% theory, respectively. In \Cref{noneigenmode}, we introduce the
% new generalization of the weak turbulence theory, which takes into
% account the contribution of noneigenmode fluctuations during the
% derivation of the particle and wave kinetic equations, resulting
% in three new terms. In \Cref{main}, we contextualize the present
% work regarding the theory discussed in the previous chapter and
% present the results obtained so far by appending the two papers
% published in this subject. In \Cref{cha:final}, we summarize the
% results and discuss the perspectives of the present research. Then,
% we propose a schedule for the remaining period until the thesis
% defense. In the end we have three appendices. \Cref{appA} shows
% an improved approximation for the second order susceptibility of
% the electrostatic bremsstrahlung for Langmuir waves. \Cref{appB}
% presents a discussion about the asymptotic equilibrium state of the
% Langmuir waves spectrum, considering a combination of a inverse
% power-law kappa distribution and a Maxwellian distribution, in the
% presence and in the absence of the electrostatic bremsstrahlung.
% The discussion in \Cref{appB} is related with the article appended
% in \Cref{appC}, which is a parallel research and is only slightly
% related with the main subject of this work, that is the study of the
% combined action of collective and collisional processes in weakly
% turbulent plasmas, in the presence of electrostatic oscillations.

\section{Astrophysical plasmas}
\label{sec:astro-plasma}
At a first glance, the study of plasmas seems completely unrelated
with

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{corona2017.png}
%    \includegraphics[0.4\textwidth]{}
    \caption{Solar corona captured during the total solar eclipse of 2017. Credit:
      \href{https://hdr-astrophotography.com/a-propos/}{Nicolas Lefaudeux}.}
    \label{fig1}
  \end{center}
\end{figure}

% In order to understand what collective processes are, one has to
% have in mind that a plasma is a many-body system composed mostly
% - or completely - of charged particles, that interact with each
% other through electromagnetic forces. Due to the long range nature
% of the electromagnetic forces, one charge can interact with several
% charges at the same time, that will interact with others, and so
% on. In such arrangement, the particle motion, at a certain volume
% element of the plasma, will be affected not only by the surrounding
% environment, but it will also be influenced by the conditions at
% distant regions of the system. This nonlocal characteristic  of the plasma
% dynamics is called \emph{collective behavior} \cite{chen}.

\chapter{Kinetic theory}
\label{sec:kin-theo}
The kinetic theory is the most fundamental description of the
plasma dynamics. Based on the concepts and methods of statistical
mechanics, together with the Maxwell equations, it provides a
formal self-consistent evolution of the plasma processes. This
formalism takes into account the variations of the velocity
distribution function $f({\bf r},{\bf v},t)$ in the phase-space
for each particle species. Statistically, this means that the
product between the distribution function and the volume element
in the hexa-dimensional phase-space $f_\alpha({\bf r},{\bf v},t)d^3r d^3v$
represents the probability of finding a particle of species
$\alpha$ in a volume element $d^3r$ around ${\bf r}$ and in a
velocity volume element $d^3v$ around ${\bf v}$, at the instant
$t$ \cite{klimo,klimon}.
